Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2024-10-21 reviews.Rmd
add excerpt

This sentence sounds exactly like P(¬E|¬H) to us.
The judgement about P(¬E|¬H) is a-priori, is about "prediction" as a statement about evidence E, given that the theory is not true (¬H).
One might argue, that it should be multiplied by ¬H perhaps? 
But that would not change any of the arguments.
In any case, we provide clear mathematical definitions for our terms.
If a reader does not agree with our terminology, they are free to term them differently.
In fact, this happens in reference to a finding we found in the meantime (Oberauer and Lewandowsky (2019)), which we added to the discussion.

>>>>

This sentence sounds exactly like $P(\neg{}E|\neg{}H)$ to us.
The judgement about $P(\neg{}E|\neg{}H)$ is a-priori, is about "prediction" as a statement about evidence E, given that the theory is not true ($\neg{}H$).
One might argue, that it should be multiplied by $\neg{}$ perhaps? 
But that would not change any of the arguments.
In any case, we provide clear mathematical definitions for our terms.
If a reader does not agree with our terminology, they are free to term them differently.
In fact, this happens in reference to a finding we found in the meantime (Oberauer and Lewandowsky (2019)), which we added to the discussion.

> Whatever the difference in evaluating preregistration as a tool, maybe conceptually more profound is that @oberauerAddressingTheoryCrisis2019 conceptualizes "discovery-oriented research" differently than we do "exploratory".
They assume the same theoretical risk ($P(\neg E| \neg H) = .05$) and detectability ($P(E| H)) = .8$) in their calculation example as we do but assign different prior probabilities, namely $.06$ for discovery versus $.6$ for theory testing.
Then, they conclude that discovery-oriented researcher requires a much lower type-I error rate to control false positive in light of the low prior probability.
This runs counter to our definition of exploratory research having low theoretical risk.
Of course, we agree that low priors require more persuasive evidence; our disagreement, therefore, lies mainly in terminology.
They imagine discovery-oriented researchers to conduct experiments where they have low expectations that they obtain positive evidence ($.06 \cdot .8 + .94 \cdot .05 = 0.095$), but if they do, it raises the posterior significantly (from $.06$ to $.51$)
In our view, researchers who set out to explore a data set often find "something" (due to low $P(\neg E| \neg H)$); therefore, it should only slightly raise your posterior if they do.
On a substantive matter, we believe both kinds of research are common in psychology.
It is, therefore, mostly a disagreement on terminology.
This disagreement only highlights why using a mathematical framework to investigate such things is so useful and ultimately indispensable because we can clearly see where and how we differ in our reasoning.
